---
title: "Heart-Attack-Analysis"
author: "Warren Yun"
date: "June 26, 2021"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls()) 
library(ggplot2)
heart_data <- read.csv("heart.csv", header = TRUE)
```

This data is from Kaggle:
https://www.kaggle.com/rashikrahmanpritom/heart-attack-analysis-prediction-dataset
```{r}
summary(heart_data)
```

Does gender have an effect on heart rate?
```{r}
male <- subset(heart_data, sex == 1)
female <- subset(heart_data, sex == 0)
```

```{r}
mean(male$thalachh, na.rm = TRUE)
mean(female$thalachh, na.rm = TRUE)

```

What about chances on a heart attack?
```{r}
length(which(male$output == 1))
length(which(female$output == 1))
```

Does age have an affect on the chance of a heart attack?
```{r}
more_likely <- subset(heart_data, output == 1)
less_likely <- subset(heart_data, output == 0)
```

Find the average age for both subsets
```{r}
mean(more_likely$age, na.rm = TRUE)
mean(less_likely$age, na.rm = TRUE)
```

Which chest pains have the greatest effect on the chances of a heart attack? \
Value 0: typical angina \
Value 1: atypical angina \
Value 2: non-anginal pain \
Value 3: asymptomatic \
\
Blue = More likely to have a heart attack \
Red = Less likely to have a heart attack \
```{r echo=FALSE}
ggplot(heart_data, aes(x = age, fill = factor(output))) + 
  geom_bar(width = 0.8) + 
  facet_wrap(~cp) + 
  ggtitle("Chest pain type") + 
  xlab("Age") +
  ylab("Total count") +
  labs("Chances of a heart attack")
```
