---
title: "Heart-Attack-Analysis"
author: "Warren Yun"
date: "June 26, 2021"
output: html_document
---

```{r setup, include=FALSE}
rm(list=ls()) 
library(ggplot2)
heart_data <- read.csv("heart.csv", header = TRUE)
```

This data is from Kaggle:
https://www.kaggle.com/rashikrahmanpritom/heart-attack-analysis-prediction-dataset

```{r}
summary(heart_data)
```

Does gender have an effect on heart rate?

```{r}
male <- subset(heart_data, sex == 1)
female <- subset(heart_data, sex == 0)
```

```{r}
mean(male$thalachh, na.rm = TRUE)
mean(female$thalachh, na.rm = TRUE)

```

What about chances on a heart attack?

```{r}
length(which(male$output == 1))
length(which(female$output == 1))
```

Does age have an affect on the chance of a heart attack?

```{r}
more_likely <- subset(heart_data, output == 1)
less_likely <- subset(heart_data, output == 0)
```

Find the average age for both subsets

```{r}
mean(more_likely$age, na.rm = TRUE)
mean(less_likely$age, na.rm = TRUE)
```

Which chest pains have the greatest effect on the chances of a heart attack? \
Value 0: typical angina \
Value 1: atypical angina \
Value 2: non-anginal pain \
Value 3: asymptomatic \
\
Blue = More likely to have a heart attack \
Red = Less likely to have a heart attack \
\
Looks like atypical agina and non-aginal pain are the types of chest pain that can raise a person's chances of a heart attack 

```{r echo=FALSE}
ggplot(heart_data, aes(x = age, fill = factor(output))) + 
  geom_bar(width = 0.8) + 
  facet_wrap(~cp) + 
  ggtitle("Chest pain type") + 
  xlab("Age") +
  ylab("Total count") +
  labs("Chances of a heart attack")
```

Does cholesterol have an effect on the maximum heart rate a person has reached? \
\
Create two subsets, one where all the patients have reached a max heart rate greater than the average max heart rate, and another where all the patients have reached a max heart rate less than the average max heart rate.

```{r}
higher_heartrate <- heart_data[which(heart_data$thalachh > mean(heart_data$thalachh)),]
lower_heartrate <- heart_data[which(heart_data$thalachh < mean(heart_data$thalachh)), ]
```

Find the average cholesterol level in both subsets

```{r}
mean(higher_heartrate$chol)
mean(lower_heartrate$chol)
```

Is there any relationship between blood sugar and maximum heart rate? \
\
Create two subsets, one where the patient's fasting blood sugar is > 120 mg/dl (1), and another where the patient's fasting blood sugar is < 120 mg/dl (0).

```{r}
higher_bs <- heart_data[which(heart_data$fbs == 1), ]
lower_bs <- heart_data[which(heart_data$fbs == 0), ] 
```

Doesn't seem to have any relationship

```{r}
mean(higher_bs$thalachh)
mean(lower_bs$thalachh)
```
